Statistical Mechanics Assignment Four

### 2016-05-24 stat_mech/latex/a4.tex
Changes to SM4

\begin{align*}
  <E> &= N\sum_{i} \epsilon_i p_i\\
  &= \frac{N}{Z}int_{-\infty}^{\infty}int_{-\infty}^{\infty}
  \frac{m(v_x^2+v_y^2)}{2}e^{-m(v_x^2+v_y^2)/2kT} dv_xdv_y\\
  &= \frac{Nm}{2kT\pi}
  \int_{0}^{\infty}\int_0^{2\pi}\frac{mv_r^2}{2}e^{-mv_r^2/2kT}}v\sin\theta dvd\theta\\
  &= \frac{Nm}{2kT\pi}
  \int_{0}^{\infty}\frac{mv_r^2}{2}e^{-mv_r^2/2kT}}v\sin\theta dvd\theta\\
\end{align*}

>>>>

\begin{align*}
  <E> &= N\sum_{i} \epsilon_i p_i\\
  &= \frac{N}{Z}\int_{-\infty}^{\infty}\int_{-\infty}^{\infty}
  \frac{m(v_x^2+v_y^2)}{2}e^{-m(v_x^2+v_y^2)/2kT} dv_xdv_y\\
  &= \frac{Nm}{2kT\pi}
  \int_{0}^{\infty}\int_0^{2\pi}\frac{mv_r^2}{2}e^{-mv_r^2/2kT}vdv_rd\theta\\
  &= \frac{Nm^2}{2kT} \int_{0}^{\infty} v_r^3e^{-mv_r^2/2kT}dv\\
  &= \frac{Nm^2}{2kT}\frac{2k^2T^2}{m^2}\\
  &= NkT\\
\end{align*}

\begin{align*}
  C_v &= \frac{d<E>}{dT} = Nk\\
\end{align*}

This is the number we expect. Because vector decomposition works on squared velocities and the
energy of an ideal gas only depends on the squared velocities of its particles, we can separate
the ideal gas energy into dimensional components and just add them up to get the total energy.
We found that each dimension has energy $\frac{1}{2}NkT$, so we get double that for our final
energy.\\
